Twisted 11-dimensional supergravity, I

### 2021-08-06 draft.tex
merge

There is a direct way to extend the Lie bracket of vector fields to the complex \eqref{eqn:cplx1}. 
Denote by $\mu$ an element of $\Omega^{0,\bu}(X , \T_X)$ and $\nu$ an element of $\Omega^{0,\bu}(X)$ (for simplicity in notation, we will not expand the anti-holomorphic dependence). 
The Lie bracket defined by the formulas
\begin{align*}
[\mu, \mu'] & = L_\mu \mu' \\
[\mu, \nu] & = L_\mu \nu 
\end{align*}
is compatible with $\div$ and endows \eqref{eqn:cplx1} with the structure of a sheaf of dg Lie algebras.\footnote{This is a local dg Lie algebra, see \cite[??]{CG2}.}

\parsec 
\ingmar{a section defining polyvector fields; not sure where this belongs}
Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
\deq{
  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
}
\ingmar{Wedges look super fucked up}
The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$. Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex. We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.

@@

Recall that an $L_\infty$ morphism $\Phi: \cL \rightsquigarrow \cL'$ is the same datum as a map of commutative dg algebras 
\deq{
  \Phi^*: C^\bu(\cL') \to C^\bu(\cL)
}
between their respective Lie algebra cochains. It follows from this that \emph{any} automorphism $\Phi$ of the free commutative algebra $C^\bu(\cL)$ defines a new model of the $L_\infty$ algebra $\cL$, for which the Chevalley--Eilenberg differential is obtained by conjugating $\d_\cL$ by~$\Phi$, and where $\Phi$ itself defines the $L_\infty$ isomorphism.

Let $\cL$ be the sheaf~\eqref{eqn:cplx1} of dg Lie algebras resolving divergence-free vector fields constructed above.
We consider the following automorphism of~$C^\bu(\cL)$, defined by its action on generators:\ingmar{notation for operators vs fields}
\deq[eq:newbase]{
%    \Psi_\infty:  \nu &\mapsto -\frac{\nu}{1-\nu}, \quad \mu \mapsto -\mu \\
    \Psi_\infty: \nu \mapsto 1 - e^{-\nu}, \quad \mu \mapsto e^\nu \mu.
}
This map defines a new model of the local $L_\infty$ algebra, which we will call $\cL_\infty$. The notation refers to the fact that this new model has nonvanishing $L_\infty$ brackets of every order. It is this new model that we will use to define the eleven-dimensional theory of twisted supergravity (as well as the family of analogous formal moduli problems on products of odd Calabi--Yau manifolds with~$\R$). 
\ingmar{I want to write the other automorphism later, I think; otherwise we have to write the composition, since we presented it on bcov}

@@

%We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
We can describe the $L_\infty$ structure on our new model $\cL_\infty$ more explicitly.
Recall that we have two types of elements: $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
The first few nonzero brackets are
\begin{align*}
[\mu]_1 & = \dbar \mu + \div \mu \\
[\mu_1,\mu_2]_2 & = \div (\mu_1 \mu_2) \\
[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
\end{align*}
For $k \geq 2$ the general formula for the $k$-ary bracket is 
\[
[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \mu_2) .
\]

We describe the explicit $L_\infty$ automorphism $\Psi \colon (\cL_0)^{L_\infty} \rightsquigarrow (\cL_0)^{strict}$ intertwining the strict dg Lie structure on $\cL_0$ and this $L_\infty$ structure.
The linear term $\Psi^{(1)} = \id$ is the identity map. 
The higher terms $\Psi^{(n)}$ are defined by 
\begin{align*}
\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=1} \nu_1 \cdots \nu_{n-1} \mu_1 . \\
\end{align*}
\brian{someone check me}

@@

\subsubsection{}
Suppose that $\fg$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\fg_k\}_{k=1,2,\ldots}$ and that $(A, \d_A)$ is a commutative dg algebra. 
The graded vector space $\fg \otimes A$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
\begin{align*}
[x \otimes a]_1 & = [x]^\fg_1 \otimes a + (-1)^{|x|} x \otimes \d_A a \\
[x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\fg_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
\end{align*}

We apply this construction, taking $\lie{g}$ to be the sheaf of dg Lie algebras resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$, as discussed above, and $A$ to be the smooth de Rham complex $(\Omega^\bu(L) , \d_L)$ where $L$ is any smooth manifold. 
We thus obtain the structure of an $L_\infty$ algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$. 
One can immediately check that this defines a local $L_\infty$ algebra on the product manifold $X \times L$.

@@

Associated to any local $L_\infty$ algebra is a classical field theory in the BV formalism that one refers to as BF theory.
We recall the construction. 
Let $\cL$ be any local $L_\infty$ algebra, it is the sheaf of sections of some graded vector bundle $L$. 
For a section $A \in \cL$, introduce the `higher curvature map' defined by the formula
\[
\mathsf{F}_A = [A]_1 + \frac12 [A,A]_2 + \frac{1}{3!} [A,A,A]_3 + \cdots .
\]

@@

The action functional reads $S_{\rm BF} = \int B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$.

\parsec
For concreteness, we recall that the fields of the theory we have constructed on $\C^{2k+1}\times\R$ are given by the sheaf $\cE$ presented in the following diagram:
\begin{equation}
  \label{eq:sympfields} 
  \begin{tikzcd}[row sep = 1 ex]
    -n & -n + 1 & -1 & 0 \\ \hline
    \Omega^{0}(X;L) \ar[r] & \Omega^{1}(X;L) & 
     \PV^{1}(X; L) \ar[r] & \PV^{0}(X; L).
\end{tikzcd}
\end{equation}
We are using the shorthand notation $\PV^{i}(X;L) = (\PV^{i,\bu}(X)\otimes \Omega^*(L), \dbar + \d_{dR}))$, so that the pairing beween $\PV^i(X;L)$ and~$\Omega^i(X;L)$ is of degree $-\dim_\C(X) -\dim_\R(L)$. As such, the $\Z$-grading indicated in~\eqref{eq:sympfields} equips the sheaf of fields with a $(-1)$-shifted symplectic structure, provided that we choose the shift to be given by
\deq{
  n = \dim_\C(X) + \dim_\R(L) - 1.
}
Note, though, that the interactions we consider do not preserve this grading, and as such only define $\Z/2\Z$-graded theories. We denote the fields $(\beta,\gamma,\mu,\nu)$ respectively.

Recall further that we constructed two equivalent descriptions of the BF theory based on divergence-free holomorphic vector fields above. Since we are now in the context of a nondegenerate BV theory, the differential is Hamiltonian, and can be incorporated into the action functional by including a quadratic term; we do this from now on. The first action functional is obtained by considering the BF theory associated to the natural dg Lie structure on the complex modeling divergence-free vector fields (inherited from the Schouten bracket). This takes the form
\deq{
  I_\strict = \beta\partial_\Omega \mu + \frac{1}{2} \gamma [\mu,\mu] + \beta[\mu,\nu].
}
The other action is of infinite order. (In fact, it is related to the BCOV action functional via a procedure we outline below.)\ingmar{or somewhere} Explicitly, this action functional is given by 
\deq{
  I_\infty = \beta \partial_\Omega \mu + \frac{1}{1-\nu} (\partial \gamma) \mu^2.
}

We demonstrated above that the two local $L_\infty$ algebras on which these BF theories are based are equivalent. As such, the BF theories are also equivalent; the map~\eqref{eq:newbase} extends uniquely to a Poisson automorphism of the Lie algebra cochains of the BF theory, which defines an equivalence of cyclic $L_\infty$ algebras. \ingmar{how should we say this} Explicitly, the map is given by
\deq{
  \nu \mapsto 1-e^{-\nu}, \ldots
}
\subsection{A family of deformations}

@@

@@

A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is a linear combination of functionals of the form
\[
\int_\Omega \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
\]
Let $k_i$ be the polyvector field type of $\alpha_i$ and let $l_j$ be the polyvector field type of $\beta_j$. 
In order for this expression to contribute nontrivially to the BCOV action two constraints must hold:
\begin{align*}
\sum_{i=1}^m k_i + \sum_{j=1}^n l_j & = d \\
\sum_{i=1}^m (1-k_i) + \sum_{j=1}^n (d-2-l_j) & = m+n-3 .
\end{align*}
The first constraint ensures that the integrand is of top polyvector degree. 
The second constraint is on the descendant degree, see \brian{ref above}.

>>>>

There is a direct way to extend the Lie bracket of vector fields to the complex \eqref{eqn:cplx1}. 
Denote by $\mu$ an element of $\Omega^{0,\bu}(X , \T_X)$ and $\nu$ an element of $\Omega^{0,\bu}(X)$ (for simplicity in notation, we will not expand the anti-holomorphic dependence). 
The Lie bracket defined by the formulas
\begin{align*}
[\mu, \mu'] & = L_\mu \mu' \\
[\mu, \nu] & = L_\mu \nu 
\end{align*}
is compatible with $\div$ and endows \eqref{eqn:cplx1} with the structure of a sheaf of dg Lie algebras.
We will refer to this sheaf by the symbol $\cL_0(X)$, or just $\cL_0$ if $X$ is understood.

The sheaf $\cL_0$ has the structure of a {\em local} dg Lie algebra, see see \cite[??]{CG2}.
This means that as a graded sheaf, $\cL_0$ is the smooth sections of a graded vector bundle and the differential and Lie bracket are given by differential and bidifferential operators, respectively.

@@

Recall that an $L_\infty$ algebra is a $\ZZ$-graded vector space $\cL$ together with the data of a square-zero, degree $+1$ derivation $\delta$ of the free commutative graded algebra $\Sym\left(\cL^\vee [-1] \right)$. 
The Chevalley--Eilenberg cochain complex is 
\[
\left(\Sym\left(\cL^\vee [-1] \right), \delta\right) .
\]
The Taylor components of $\delta$ define higher brackets $\{[-]_k\}_{k=1,2,\ldots}$ where $[-]_k \colon \cL^{\times k} \to \cL[2-k]$.

An $L_\infty$ morphism $\Phi: \cL \rightsquigarrow \cL'$ is the same datum as a map of commutative dg algebras 
\deq{
  \Phi^*: \clie^\bu(\cL') \to \clie^\bu(\cL)
}
between their respective Lie algebra cochains. It follows from this that \emph{any} automorphism $\Phi$ of the free commutative algebra on $\cL^\vee[-1]$ defines a new model of the $L_\infty$ algebra $\cL$, for which the Chevalley--Eilenberg differential is obtained by conjugating $\delta_\cL$ by~$\Phi$, and where $\Phi$ itself defines the $L_\infty$ isomorphism.

$\cL_0$ is the sheaf~\eqref{eqn:cplx1} resolving divergence-free vector fields equipped with the dg Lie algebra structure constructed in the previous section.
We consider the following automorphism of~$\Sym(\cL_0^\vee[-1])$, defined by its action on generators:\ingmar{notation for operators vs fields}
\deq[eq:newbase]{
%    \Psi_\infty:  \nu &\mapsto -\frac{\nu}{1-\nu}, \quad \mu \mapsto -\mu \\
    \Psi_\infty: \nu \mapsto 1 - e^{-\nu}, \quad \mu \mapsto e^{-\nu} \mu.
}
This map defines a new model of the $L_\infty$ algebra with underlying graded vector space the same as \eqref{eqn:cplx1}, which we will call $\cL_\infty$. 
The formulas for the automorphism above clearly arise from maps of vector bundles and hence endow $\cL_\infty$ with the structure of a local $L_\infty$ algebra, meaning all operations are given by polydifferential operators.

The notation refers to the fact that this new model has nonvanishing $L_\infty$ brackets of every order. 
It is this new model that we will use to define the eleven-dimensional theory of twisted supergravity (as well as the family of analogous formal moduli problems on products of odd Calabi--Yau manifolds with~$\R$).

@@

%We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
We can describe the $L_\infty$ structure on our new model $\cL_\infty$ more explicitly.
Recall that we have two types of elements: $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
The first few nonzero brackets are
\begin{align*}
[\mu]_1 & = \dbar \mu + \div \mu \\
[\mu_1,\mu_2]_2 & = \div (\mu_1 \mu_2) \\
[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
\end{align*}
\brian{coefficients}
For $k \geq 2$ the general formula for the $k$-ary bracket is 
\[
[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \mu_2) .
\]

%We describe the explicit $L_\infty$ automorphism $\Psi \colon (\cL_0)^{L_\infty} \rightsquigarrow (\cL_0)^{strict}$ intertwining the strict dg Lie structure on $\cL_0$ and this $L_\infty$ structure.
%The linear term $\Psi^{(1)} = \id$ is the identity map. 
%The higher terms $\Psi^{(n)}$ are defined by 
%\brian{someone check me}
%\begin{align*}
%\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=1} \nu_1 \cdots \nu_{n-1} \mu_1 . \\
%\end{align*}

\parsec
There is yet another $L_\infty$ model for divergence-free vector fields that we remark on here.
\ingmar{I want to write the other automorphism later, I think; otherwise we have to write the composition, since we presented it on bcov}

@@

\parsec
Suppose that $\cL$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\cL_k\}_{k=1,2,\ldots}$ and that $(A, \d_A)$ is a commutative dg algebra. 
The graded vector space $\cL \otimes A$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
\begin{align*}
[x \otimes a]_1 & = [x]^\cL_1 \otimes a + (-1)^{|x|} x \otimes \d_A a \\
[x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\cL_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
\end{align*}

We apply this construction, taking $\cL$ to be the sheaf resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ equipped with either the strict dg Lie algebra structure $\cL_0(X)$ or its non-strict $L_\infty$ structure $\cL_\infty (X)$. 
The algebra $A$ will be the smooth de Rham complex $(\Omega^\bu(L) , \d_L)$ where $L$ is any smooth manifold.

We thus obtain the structure of an dg Lie algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$ or an $L_\infty$ algebra $\cL_\infty(X) \otimes \Omega^\bu(L)$.
These define equivalent local $L_\infty$ algebras on the product manifold $X \times L$.

@@

Associated to any local $L_\infty$ algebra is a classical field theory in the BV formalism that one refers to as BF theory.
We recall the construction. 
Let $\cL$ be any local $L_\infty$ algebra on some manifold $M$, it is the sheaf of sections of some graded vector bundle $L$. 
For a section $A \in \cL$, introduce the `higher curvature map' defined by the formula
\[
\mathsf{F}_A = [A]_1 + \frac12 [A,A]_2 + \frac{1}{3!} [A,A,A]_3 + \cdots .
\]

@@

The action functional reads $S_{\rm BF} = \int_M B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$.

We thus obtain a theory in the BV formalism on the product manifold $X \times L$ associated to both local $L_\infty$ algebras $\cL_0(X) \otimes \Omega^{\bu}(L)$ and $\cL_\infty(X) \otimes \Omega^\bu(L)$.

\parsec
For concreteness, we spell out the fields of the theories we have constructed on $X \times L$.
In both cases, the space of fields equipped with the linear BRST operator is
\begin{equation}
  \label{eq:sympfields} 
  \begin{tikzcd}[row sep = 1 ex]
    -n & -n + 1 & -1 & 0 \\ \hline
    \Omega^{0,\bu}(X;L) \ar[r, "\del"] & \Omega^{1,\bu}(X;L) & 
     \PV^{1,\bu}(X; L) \ar[r, "\div"] & \PV^{0,\bu}(X; L).
\end{tikzcd}
\end{equation}
We denote the fields $(\beta,\gamma,\mu,\nu)$ respectively.
We are using the shorthand notation $\PV^{i}(X;L) = (\PV^{i,\bu}(X)\otimes \Omega^\bu(L), \dbar + \d_{L}))$.

The natural pairing between $\PV^i(X;L)$ and~$\Omega^i(X;L)$ is of degree $-\dim_\C(X) -\dim_\R(L)$. 
As such, the $\Z$-grading indicated in~\eqref{eq:sympfields} equips the sheaf of fields with a $(-1)$-shifted symplectic structure, provided that we choose the shift to be given by
\deq{
  n = \dim_\C(X) + \dim_\R(L) - 1.
}

We have constructed two equivalent descriptions of the BF theory which share the linear BRST complex \eqref{eq:sympfields}.

Explicitly, the action functional for BF theory associated to the local dg Lie algebra $\cL_0(X) \otimes \Omega^{\bu}(L)$ is
\deq{
  S_\strict = \int^\Omega \beta (\dbar + \d_L) \nu + \int^\Omega \gamma (\dbar + \d_L) \mu + \int^\Omega \beta\partial_\Omega \mu + \frac{1}{2} \int^\Omega \gamma [\mu,\mu] + \int^\Omega \beta[\mu,\nu].
}
As in the Lie algebra structure of this strict model, notice that the Schouten--Nijenhuis bracket appears explicitly.

The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(L)$ is of infinite order. 
(In fact, it is related to the BCOV action functional via a procedure we outline below.)\ingmar{or somewhere} 
Explicitly, this action functional is
\deq{
  S_\infty = \int^\Omega \beta (\dbar + \d_L) \nu + \int^\Omega \gamma (\dbar + \d_L) \mu + \frac12 \int^\Omega \beta \partial_\Omega \mu + \int^\Omega\frac{1}{1-\nu} (\partial \gamma) \mu^2.
}

We demonstrated above that the two local $L_\infty$ algebras on which these BF theories are based are equivalent. As such, the BF theories are also equivalent; the map~\eqref{eq:newbase} extends uniquely to an automorphism of BV theories.
Explicitly, the automorphism is
\begin{multline}
  \mu \mapsto e^{-\nu} \mu, \qquad \nu \mapsto 1-e^{-\nu} \\
  \beta \mapsto (\beta - \mu \gamma) e^{\nu},\qquad \gamma \mapsto e^{\nu} \gamma .
\end{multline}
\subsection{A family of deformations}

@@

\parsec[sec:pv] 
\ingmar{a section defining polyvector fields; not sure where this belongs}
Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
\deq{
  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
}
\ingmar{Wedges look super fucked up}
The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$. Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex. We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.

@@

A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is a linear combination of functionals of the form
\[
\int^\Omega \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
\]
Let $k_i$ be the polyvector field type of $\alpha_i$ and let $l_j$ be the polyvector field type of $\beta_j$. 
In order for this expression to contribute nontrivially to the BCOV action two constraints must hold:
\begin{align*}
\sum_{i=1}^m k_i + \sum_{j=1}^n l_j & = d \\
\sum_{i=1}^m (1-k_i) + \sum_{j=1}^n (d-2-l_j) & = m+n-3 .
\end{align*}
The first constraint ensures that the integrand is of top polyvector degree. 
The second constraint is on the descendant degree, see \brian{ref above}.
